Computing Entropies With Nested Sampling

### 2017-07-10 paper/ms.tex
More Pareto writing

With heavy-tailed distributions, it can be difficult to predict future
observations from past ones, for two reasons. First, the observations may not
provide much information about the parameters (in this case, $\alpha$), and
second, even conditional on the parameters, the predictive distribution for
future data can be heavy-tailed, implying a lot of uncertainty.

>>>>

With heavy-tailed distributions, it can be difficult to predict future
observations from past ones, for two reasons. First, the observations may not
provide much information about the parameters (in this case, $\alpha$), and
second, even conditional on the parameters, the predictive distribution for
future data can be heavy-tailed, implying a lot of uncertainty. However, there
data clearly provides {\em some} information about the future.

Consider $n=100$ data values, partitioned into two halves, so
$\boldsymbol{y} = \{x_1, ..., x_{50}\} = \{y_1, ..., y_{50}\}$
is the first half of the data and
$\boldsymbol{z} = \{x_{51}, ..., x_{100}\} = \{z_1, ..., z_{50}\}$
is the second half. Let $\bar{y}$ and $\bar{z}$ be the averages of the two
subsets of the data:
\begin{align}
\bar{y} &= \frac{1}{50} \sum_{i=1}^{50} y_i \\
\bar{z} &= \frac{1}{50} \sum_{i=1}^{50} z_i.
\end{align}
In this section we use the algorithm to answer the questions:
i) How uncertain is $\bar{y}$?; ii) How uncertain is $\bar{z}$; and
iii) How informative is $\bar{y}$ about $\bar{z}$? These are quantified by
$H(\bar{y})$, $H(\bar{z})$, and $I(\bar{y}; \bar{z})$ respectively. This can
be done despite the fact that $\alpha$ is unknown.

\subsection{}
